Carbonate chemistry at Ny-Ålesund

### 2021-12-27 awipev-CO2.Rmd
added code to read Philipp's files but not used in the end

# # Many issue with sal_ctd_insi
# # read files made available by Philipp on 2021-12-09 with quality-controlled data
# # not useful as these are FerryBox data...
# https://dashboard.awi.de/?dashboard=3865
# Test with one of the files: https://doi.org/10.1594/PANGAEA.929583
# pg_data("10.1594/PANGAEA.929583")

>>>>

# # Many issue with sal_ctd_insi
# # read files made available by Philipp on 2021-12-09 with quality-controlled data
# # not useful as these are FerryBox data...
# https://dashboard.awi.de/?dashboard=3865
# # NOT USED
# file_list <- c("10.1594/PANGAEA.896828", "10.1594/PANGAEA.896822", "10.1594/PANGAEA.896821", "10.1594/PANGAEA.896771", "10.1594/PANGAEA.896770", "10.1594/PANGAEA.896170", "10.1594/PANGAEA.897349", "10.1594/PANGAEA.927607", "10.1594/PANGAEA.929583")
# i <- 0; tmp <- NULL
# for (i in 1:length(file_list)) {
#     z <- pg_data(file_list[i])
#     tmp <- dplyr::bind_rows(tmp, z[[1]]$data)
# }
# tmp <- tmp %>% 
#   dplyr::mutate(datetime = lubridate::parse_date_time(tmp$`Date/Time`,
#                 orders = "ymd HM")) %>% 
#   dplyr::select(datetime, `Sal (PSU)`, `Temp [°C]`) %>% 
#   dplyr::arrange(datetime) %>% 
#   dplyr::distinct(datetime, .keep_all = TRUE) %>%  # there are a few duplicated datetime
#   as_tsibble(index = datetime)
# eff <- dplyr::left_join(d_hour, tmp, by = "datetime")
